A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Changes in V

\section{Corpus of R Programs}

We have assembled a corpus of \CorpusPackages R packages and
\CorpusFinishedKaggle user-written data-analysis scripts. Together it contains
\CorpusAllCodeRnd lines of source code\footnote{Excluding comments and blank lines using \url{github.com/AlDanial/cloc}}.

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran).
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@

>>>>

\section{Corpus}

We now describe the corpus used in this study.

\begin{figure*}[!tb]\centering\includegraphics[width=\linewidth]
  {corpus.pdf}\caption{CRAN packages}\label{fig:corpus}
\end{figure*}

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran)\footnote{Excluding comments and blank lines using \url{github.com/AlDanial/cloc}}.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@

\subsection{Summary}

Together, we have assembled a corpus of \CorpusPackages R packages and
\CorpusFinishedKaggle user-written data-analysis scripts. Together it contains
\CorpusAllCodeRnd lines of source code (both and R and native code). Out of
this, \CorpusAllRunnbaleCode lines R code spread across \CorpusAllPrograms R
scripts is the code that we run during the dynamic analysis.
